MADA Project Part 2

### 2024-04-26 R/processing-code/MADAproject_pt2_ruiz.qmd
testing changes

# Construct the path to the veterinary case data file
file_path_vet <- here("data", "processed-data", "animal_cases.xlsx")

@@

# Calculate the average number of MEL by year
average_mel_by_year <- trap_proportion %>%
  group_by(Year) %>%
  summarise(Average_MEL = mean(MEL, na.rm = TRUE))

>>>>

# Construct the path to the veterinary case data file
file_path_vet <- here("data", "raw-data", "animal_cases.xlsx")

@@

# Calculate the average number of MEL by year
average_mel_by_year <- trap_wide_data %>%
  group_by(Year) %>%
  summarise(Average_MEL = mean(MEL, na.rm = TRUE))
